Approximate Sequencing of Virtual Reels with Genetic Algorithms

### 2020-06-20 Approximate-Sequencing-of-Virtual-Reels-with-Genetic-Algorithms/paper.tex
A full text of the paper was written.

Estimation of the fitness value is done by calculation of average Euclidean distance for a sorted set of chunks in the candidate and the original as pairs. Sorting is done in order for candidate chunks to correspond to original chunks when Euclidean distance is calculated between the pairs. Original chunks are sorted only once when they are collected as samples. The candidate chunks are sorted each time when the candidate sequence is changed (crossover and/or mutation). All distances between chunk pairs are summed and divided by chunks number in order for the average value to be offered as chromosome fitness.

@@

@@

>>>>

Estimation of the fitness value is done by calculation of average Euclidean distance for a sorted set of chunks in the candidate and the original as pairs. Sorting is done in order for candidate chunks to correspond to original chunks when Euclidean distance is calculated between the pairs. Original chunks are sorted only once when they are collected as samples. The candidate chunks are sorted each time when the candidate sequence is changed (crossover and/or mutation). All distances between chunk pairs are summed and divided by chunks number in order for the average value to be offered as chromosome fitness. Average Euclidean distance is taken with a negative sign because as far is the candidate solution from the original as low is the chromosome fitness. By acceptance of this fitness value estimation, it means that fitness value of the original distanced with itself will be zero which is the highest possible fitness value.

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{fig01}
\caption{Original sequences of five virtual reels}
\label{fig:01}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{fig02}
\caption{Reconstructed sequences of five virtual reels}
\label{fig:02}
\end{figure}

@@

All experiments are done with a custom-created software project published in GitHub \cite{Balabanov-2020}. The source code is written in Java 8 as programming language. An empirical population of 137 individuals is chosen. The mutation rate is chosen to be 0.05\% as a recommended value in the literature. Modified competitive selection is implemented where the crossover rate is almost 100\%. Uniform crossover with a normally distributed participation threshold is chosen (mean of 50\% and standard deviation of 20\%). If the offspring is better than the worst of three individuals it takes its place and elitism rule is applied indirectly.

A set of 8 different virtual reels is used as input data of original sequences. Visual representation of one of them is presented in Fig. \ref{fig:01}. Each of the five virtual reels is reconstructed separately. The result of the reconstructed reels is shown in Fig. \ref{fig:02}. The genetic algorithm is stated for 100 generations. It is clearly visible that reconstructed sequences are pretty different in length than the original once. Fitness values for the five reconstructed reels are as follows: -3.521716216163723, -4.310895779885775, -2.3809034389618526, -3.8553857718048152, -3.6797186696978517.

In current experiments, only a single run of genetic algorithm is done, but many consecutive runs (simulated annealing as an analogy) will improve the achieved optimality because genetic algorithms can be stuck in local optimums.
